---
title: "Lecture_1"
author: "Trinity SHI"
date: "November 10 2025"
output: 
  rmarkdown::html_document:
    toc: true
  vignette: > 
    %\\VignetteIndexEntry{R markdown}
    %\\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---


##Dependencies

This document depends on the following packages:
```{r}
library(devtools)
library(knitr)
```
##Make the code pretty
Set the color scheme and pch.
```{r}
# Color scheme inspired by the RSkittleBrewer package
tropical = c('darkorange', 'dodgerblue', 'hotpink', 'limegreen', 'yellow')
palette(tropical)
par(pch = 19)
```

Line by line explanantion of the Code:
1) c() -> As learnt from other projects as well, this function not only allows for rules such as replacing characters c( A = "T"), but also combining datas together to form a collective list/vector c(Lits_1, List2), which is very useful for creating data frames. 
2) palette() -> It stores the colors that will be used for graphics, so now if I use plot() or ggplot2() the col argument in plotting functions(e.g., col=1 for the first color in the palette).
3) par() -> Used to set the plotting character (symbol) for points in plots created using base R graphics functions.  In this case 19 is hollow circles. 

But unfortunately, for R markdown files the pch won't propagate unless you do something that is a little bit messy. 
```{r, echo = FALSE }
knit_hooks$set(setPch = function(before, options, envir)
{
  if(before) par(pch = 19)
})
opts_chunk$set(setPch = TRUE)
```

The following will also be hid for future documents but keep in mind it shows how to set a default figure width and height, as well as setting plot margians.
```{r, echo = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 5, size = "footnotesize", warning = FALSE, message = FALSE)

knitr::opts_chunk$set(small.mar = function(before, option, envir)
  {
  if (before)
  {
    graphics :: par(mar = c(5,5,1.5,1))
  }
})
```

#Compiling Questions in Course:
1. Try compiling this document using the “Knit HTML” button. What files are produced?
      It knits to a html document.
2. Edit the output to be “pdf_document” and recompile. What files are produced?
      It knits to a pdf document.
3. Edit the output to be “word_document” and recompile. What files are produced?
      It knits to a word document.
      
##Naming Code Chunks
Annotations for the header of the chunk:
*The label “chunk1” after "r" in {} tells you which part of the code was running in case you have errors.
*The label "echo = FALSE" will hide this chunk of code from the knit. 
*The label "cache = TRUE" makes it so that the code won't take as long to compile the second time.  
```{r, chunk1}
x = rnorm(100)
plot(x, col = 2)
```
*Using asterix gives you a bullet point.

##Session Information
It is very useful to record the session information when performing analyses so you can collaborate with yourself in the future.
```{r, cache = TRUE}
sessionInfo()
```

```{r, cache = TRUE}
devtools :: session_info()
```
## Some Notes:
* :: seems to follow a package name explicitly stating "I want to access THIS package for THIS function", I think its used to access package specific functions when multiple packages share the same name of a function.
* knitr::opts_chunk$set() very useful to setup the default environment for graphs, so they share the same rules (margin, color, style, heading, etc)
